Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-15 paper-ieee-trans.tex
fix typo

\begin{table*}[!h]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Features on software reliability in EC-projects}
\label{tab:feat}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{llllllll}
\hline
\hline
Feature & DataGrid & EGEE I, II, III & ETICS 1, 2 & EMI & EGI-Inspire & EGI Engage & INDIGO-DataCloud\\
\hline
\hline
Architecture Task Force&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Communication Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Requirements Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Agile Methodologies&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Buu/Test Management Procedure&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Manual Certification Procedure&$\surd$&$\surd$&&$\surd$&&&\\
Automatic Certification Tool&&&$\surd$&&$\surd$&$\surd$&$\surd$\\
Auto-generated Documentation&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Software Product Metrics&$\surd$&$\surd$&$\surd$&&$\surd$&$\surd$&$\surd$\\
Quality Criteria Definition&&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
\hline
\hline
\end{tabular}
\end{table*}

@@

Last but not least, as described in section \ref{sec:devops}, in order
to facilitate the usage of the INDIGO--DataCloud services, they can be deployed
automatically using either Ansible \cite{indigo-ansible} or Puppet
\cite{indigo-puppet} open--source configuration tools. The adoption of such Configuration Management
tools not only eases the consumption of the products developed by external users or
infrastructures, but also tackles the correct installation and configuration of the
services and applications. A representative example is the \textit{50 roles} being 
developed within the project and currently hosted in the Ansible Galaxy portal for 
the project \footnote{https://galaxy.ansible.com/indigo-dc/}.

>>>>

\begin{table*}[!h]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Features on software reliability in EC-projects}
\label{tab:feat}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{llllllll}
\hline
\hline
Feature & DataGrid & EGEE I, II, III & ETICS 1, 2 & EMI & EGI-Inspire & EGI Engage & INDIGO-DataCloud\\
\hline
\hline
Architecture Task Force&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Communication Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Requirements Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Agile Methodologies&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Build/Test Management Procedure&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Manual Certification Procedure&$\surd$&$\surd$&&$\surd$&&&\\
Automatic Certification Tool&&&$\surd$&&$\surd$&$\surd$&$\surd$\\
Auto-generated Documentation&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Software Product Metrics&$\surd$&$\surd$&$\surd$&&$\surd$&$\surd$&$\surd$\\
Quality Criteria Definition&&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
\hline
\hline
\end{tabular}
\end{table*}

@@

Last but not least, as described in section \ref{sec:devops}, in order
to facilitate the usage of the INDIGO--DataCloud services, they can be deployed
automatically using either Ansible \cite{indigo-ansible} or Puppet
\cite{indigo-puppet} open--source configuration tools. The adoption of such Configuration Management
tools not only eases the consumption of the products developed by external users or
infrastructures, but also tackles the correct installation and configuration of the
services and applications. A representative example is the number of roles currently
hosted in the Ansible Galaxy portal for the project [ref].
